---
title: "CodeBook"
output: html_document
---
# Getting and Cleaning Data Project

### Variables and their observation

```{r echo=FALSE}
Variable <- c("Subject", "Metrics", "Activity", "Features","Measurement Subsets")
Var_Frequency <- c(30, 24, 6, 561,2)
VariableTable <- as.data.frame(cbind(Variable, Var_Frequency))
VariableTable
```

### List of mertrics labelled as FEATURES

```{r echo=FALSE}
Metrics <- read.csv("/Users/Mood/Documents/Getting-and-cleaning-Data/metrics.csv")
Metrics
```

### List of activities during which metrics/features are recorded using either an accelerometer or a gyroscope

```{r echo=FALSE}
Activity <- c("WALKING", "WALKING_UPSTAIRS", "WALKING_DOWNSTAIRS", "SITTING", "STANDING", "LAYING")
Activity
```


### Data sets description
##### Data are collected from 8 datasets, in which 6 have 2 subsets: Training & Test. 70% of observation will be stored as "training" observation, with the balance labelled under "Testing". Data sets include:
##### - 'features_info.txt': Shows information about the variables used on the feature vector.
##### - 'features.txt': List of all features.
##### - 'activity_labels.txt': Links the class labels with their activity name.
##### - 'train/X_train.txt': Training set.
##### - 'train/y_train.txt': Training labels.
##### - 'test/X_test.txt': Test set.
##### - 'test/y_test.txt': Test labels.


### Data processing & treament
##### - The training and test subsets are merged
##### - Columns are renamed to ease the data handling
##### - Columns with data related to the standard deviation or the mean are isolated in a new dataset (MegaDataSet)
##### - The resulting table is then  grouped by subjects and activities to calculate their respective means.
##### - Columns are renamed again to ease the reading of the metrics/features.
